Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-31 SupportingInformation.Rmd
minor edits

 [@Sheppard2017] converted monthly values to yearly values by averaging over all months. But here we only allowed maximum 4 months in a year with missing data which were replaced by median value for that month (drawn from all years in which data was available). We used data from 14 locations which had atleast 45 years time series data (see Figure \ref{SM-fig_plankton_map}).

 The Great Miami Wetland Mitigation Bank  was at $36^{\circ}46^{'}51^{''}$ N, $84^{\circ}20^{'}26^{''}$ W) in Trotwood, Montgomery County, Ohio. Additional information on the history of the site and soil types is detailed in @Jarecke2016. Briefly, the closed static flux chamber method was used [@Holland1999] to measure $CH_{4}$ fluxes at 28 locations across a hydrologic gradient (upland to seasonal wetland) at daily to weekly interval from September 2015 to September 2016. **See and Smyth et al, pending for
additional details???** on greenhouse gas flux methods for this site. We considered 13 locations that had atleast 50 dates data.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6 cm,height=6 cm]{./stat_image.jpg} \hspace{0.6 cm}
\caption[For definitions of nonparametric statistics]{Schematic diagram supporting definitions of nonparametric tail dependence statistics. The red and blue lines are, respectively, $u+v=2l_b$ and $u+v=2u_b$.\label{fig_stat_image}}
\end{center}
\end{figure}

@@

N and F copula families 
are known to have symmetric tail dependence,
i.e., strengths of dependence in the lower and upper tails are the same, for all copulas
in these families [@nelsen2006_copula]. C copulas are known to have stronger lower- than 
upper-tail dependence, and SC copulas, being rotations of C copulas by 
$180^\circ$, have stronger upper- than lower tail dependence [@nelsen2006_copula].
Using the `iRho` function from the `copula` package, for each of the four families N, 
F, C, and SC, we obtained parameters for which the expected value of 
Spearman's $\rho$ was, separately, $0,0.1,0.2,...,0.9$. For each copula family and for each 
of the selected parameter values we generated  $n$ points, 100 times, and thereby 
computed 100 values of the 
statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$. This exercise 
was repeated, separately, 
for $n=1000$ and for $n=35$, these cases being chosen, respectively, to reflect 
asymptotic behavior of the 
statistics and their behavior on the small datasets which are common in some fields
of ecology. The mean and standard error of the three difference statistics were computed for 
each copula family, parameter value, and value of $n$, and results were plotted against 
Spearman's rho (Figs \ref{fig_stat_testing35} and \ref{fig_stat_testing1000}), 
the expectation being that the difference statistics would be positive for 
C copulas, negative for SC copulas (except for the case of $\rho=0$, a 
boundary case of these families corresponding to independence), and not significantly different 
from $0$ for F and N 
copulas.
We used a $t$-test with a significance threshold of $0.05$ to judge signficance here.
These expectations were fullfilled (Figs \ref{fig_stat_testing35} and 
\ref{fig_stat_testing1000}).

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt35_rankT.pdf}
\caption[Testing nonparametric statistics with 35 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the C and SC copulas, and the known symmetry of tail dependence of the N and F copulas. See Appendix  \ref{Test_npa_stat} for details. $n=35$. \label{fig_stat_testing35}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt1000_rankT.pdf}
\caption[Testing nonparametric statistics with 1000 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the C and SC copulas, and the known symmetry of tail dependence of the N and F copulas. See Appendix  \ref{Test_npa_stat} for details. $n=1000$.\label{fig_stat_testing1000}}
\end{center}
\end{figure}

@@

For bivariate datasets, surrogates were produced as follows.

- Given data $(x_i,y_i)$ for $i=1,\ldots,n$ and a 
one-parameter target copula family $\mathcal{B}(\theta)$ (here $\theta$ denotes the parameter), let $\tau$ be the
Kendall correlation of the $x_i$ with the $y_i$ and find the parameter value $\theta_\tau$ for which 
$\mathcal{B}(\theta_\tau)$ has Kendall correlation $\tau$ (this is possible for the one-parameter copula families of this 
study using the `iTau` function of the `VineCopula` package). 
- Generate data $(a_i,b_i)$, $i=1,\ldots,n$ from 
$\mathcal{B}(\theta_\tau)$. 
- Permute the ordered set $(x_1,\ldots,x_n)$ such that the permutation
$(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ has $\rank(x_{\sigma_x(i)})$ equal to $\rank(a_i)$ for all $i$, where 
$\rank(x_{\sigma_x(i)})$ is the rank of $x_{\sigma_x(i)}$ in the set $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$, and
$\rank(a_i)$ is the rank of $a_i$ in the set $(a_1,\ldots,a_n)$ (here $\sigma_x$ is a permutation of the 
indices $1,\ldots,n$). 
- Likewise permute $(y_1,\ldots,y_n)$
such that the permutation
$(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ has $\rank(y_{\sigma_y(i)})$ equal to $\rank(b_i)$ for all $i$ ($\sigma_y$ is 
another permutation of $1,\ldots,n$).
- The surrogate dataset is $(x_{\sigma_x(i)},y_{\sigma_y(i)})$ for $i=1,\ldots,n$.

\noindent Our code for this algorithm is `copsurrog2d` in the 
`BIVAN` repository (https://github.com/sghosh89/BIVAN). 
Because $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ 
is a permutation of $(x_1,\ldots,x_n)$ and $(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ is a 
permutation 
of $(y_1,\ldots,y_n)$, the marginal distributions of the surrogate data are exactly the same as 
those of the original data. 
Because ranks of the surrogate data are matched to ranks of the $a_i$ and $b_i$, the
Kendall correlation of the surrogate dataset will be the same as that of the $a_i$ and $b_i$, and therefore 
will be close to $\tau$ (differences arising only through sampling variation). If instead of $\theta_\tau$
a parameter value $\theta_\rho$ is used such that the Spearman correlation of $\mathcal{B}(\theta_\rho)$ is the same
as that of the $x_i$ with the $y_i$, then Spearman correlations of surrogates will very nearly equal (except for 
sampling variation) the Spearman correlation of the empirical data.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_soilCN/soilCN_bivfunctionplot.pdf}
\caption[Nonparametric tests against an N-copula null, soil C and N data]{Nonparametric tests for tail dependence and other deviations from N-copula structure, for soil C and N data. As described in the main text, the values of the statistics $\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$ and $\Dsq_{l_b,u_b}$ for real data (red crosses) were compared to distributions of their values on 1000 Kendall- or Spearman-preserving N surrogates of the data (blue and green x's show 0.025 and 0.975 quantiles), separately in two comparisons for each of the ranges $(l_b,u_b)=(0,0.1),\ldots,(0.9,1)$. Whenever the red cross was outside the range given by the x's, text at the top of panels indicates the number of surrogate values the real-data value was greater than or less than. For instance, a value $>N$ (respectively, $<N$) means the value of the statistic on real data was greater than (respectively, less than) its value on $N$ surrogates. When the statistic was greater than 975 or less than 975 surrogate values, it indicates significance ($95\%$ confidence level). When $\cor$ or $\Ps$ values (respectively, $\Dsq$ values) were greater than surrogates, it means dependence in that part of the distributions was stronger than (respectively, weaker than) expected from a normal-copula null hypothesis. \label{fig_soilCN_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/BMR_results/birds/birds_numbin_10_bivfunctionplot.pdf}
\caption[Nonparametric tests against an N-copula null, bird body mass and BMR data]{Nonparametric tests for tail dependence and other deviations from N-copula structure, for bird body mass and BMR data. Same format as Fig. \ref{fig_soilCN_nonparam}, see caption of that figure. \label{fig_bmr_birds_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/BMR_results/mammals/mammals_numbin_10_bivfunctionplot.pdf}
\caption[Nonparametric tests against an N-copula null, mammal body mass and BMR data]{Nonparametric tests for tail dependence and other deviations from N-copula structure, for mammal body mass and BMR data. Same format as Fig. \ref{fig_soilCN_nonparam}, see caption of that figure. \label{fig_bmr_mammals_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Ceder_creek_results/2000cc_numbin_10_bivfunctionplot.pdf}
\caption[Nonparametric tests against an N-copula null, Cedar Creek data]{Nonparametric tests for tail dependence and other deviations from N-copula structure, for Cedar Creek data. Same format as Fig. \ref{fig_soilCN_nonparam}, see caption of that figure.\label{fig_cc2000_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.4 cm} (D)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Corl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{3.4 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.4 cm} (H)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Pl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_D2u_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{5.4 cm} (I) \hspace{3.4 cm} (J) \hspace{3.2 cm} (K) } \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption[Nonparametric tail statistics versus distance between locations for green spruce aphid abundance data]{Nonparametric tail statistics versus great-circle distance, $D$, between sampling locations for green spruce aphid abundance data. \label{fig_aphid_count}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.4 cm} (D)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{3.4 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.4 cm} (H)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{5.4 cm} (I) \hspace{3.4 cm} (J) \hspace{3.2 cm} (K) } \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption[Nonparametric tail statistics versus distance between locations for leaf-curling plum aphid first flight data]{Nonparametric tail statistics versus great-circle distance, $D$, between sampling locations for leaf-curling plum aphid first flight data. \label{fig_aphid_ff}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.4 cm} (D)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{3.4 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.4 cm} (H)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{5.4 cm} (I) \hspace{3.4 cm} (J) \hspace{3.2 cm} (K) } \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption[Nonparametric tail statistics versus distance between locations for \textit{Ceratium furca} abundance data]{Nonparametric tail statistics versus great-circle distance, $D$, between sampling locations for \textit{Ceratium furca} abundance data. \label{fig_pns}}
\end{center}
\end{figure}

>>>>

 [@Sheppard2017] converted monthly values to yearly values by averaging over all months. But here we only allowed maximum 4 months in a year with missing data which were replaced by median value for that month (drawn from all years in which data was available). We used data from 14 locations which had at least 45 years time series data (see Figure \ref{SM-fig_plankton_map}).

 The Great Miami Wetland Mitigation Bank  was at $36^{\circ}46^{'}51^{''}$ N, $84^{\circ}20^{'}26^{''}$ W) in Trotwood, Montgomery County, Ohio. Additional information on the history of the site and soil types is detailed in @Jarecke2016. Briefly, the closed static flux chamber method was used [@Holland1999] to measure $CH_{4}$ fluxes at 28 locations across a hydrologic gradient (upland to seasonal wetland) at daily to weekly interval from September 2015 to September 2016. **See and Smyth et al, pending for
additional details???** on greenhouse gas flux methods for this site. We considered 13 locations that had at least 50 dates data.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6 cm,height=6 cm]{./stat_image.jpg} \hspace{0.6 cm}
\caption[For definitions of non-parametric statistics]{Schematic diagram supporting definitions of non-parametric tail dependence statistics. The red and blue lines are, respectively, $u+v=2l_b$ and $u+v=2u_b$.\label{fig_stat_image}}
\end{center}
\end{figure}

@@

N and F copula families 
are known to have symmetric tail dependence,
i.e., strengths of dependence in the lower and upper tails are the same, for all copulas
in these families [@nelsen2006_copula]. C copulas are known to have stronger lower- than 
upper-tail dependence, and SC copulas, being rotations of C copulas by 
$180^\circ$, have stronger upper- than lower tail dependence [@nelsen2006_copula].
Using the `iRho` function from the `copula` package, for each of the four families N, 
F, C, and SC, we obtained parameters for which the expected value of 
Spearman's $\rho$ was, separately, $0,0.1,0.2,...,0.9$. For each copula family and for each 
of the selected parameter values we generated  $n$ points, 100 times, and thereby 
computed 100 values of the 
statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$. This exercise 
was repeated, separately, 
for $n=1000$ and for $n=35$, these cases being chosen, respectively, to reflect 
asymptotic behavior of the 
statistics and their behavior on the small data sets which are common in some fields
of ecology. The mean and standard error of the three difference statistics were computed for 
each copula family, parameter value, and value of $n$, and results were plotted against 
Spearman's rho (Figs \ref{fig_stat_testing35} and \ref{fig_stat_testing1000}), 
the expectation being that the difference statistics would be positive for 
C copulas, negative for SC copulas (except for the case of $\rho=0$, a 
boundary case of these families corresponding to independence), and not significantly different 
from $0$ for F and N 
copulas.
We used a $t$-test with a significance threshold of $0.05$ to judge significance here.
These expectations were fulfilled (Figs \ref{fig_stat_testing35} and 
\ref{fig_stat_testing1000}).

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt35_rankT.pdf}
\caption[Testing non-parametric statistics with 35 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the C and SC copulas, and the known symmetry of tail dependence of the N and F copulas. See Appendix  \ref{Test_npa_stat} for details. $n=35$. \label{fig_stat_testing35}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_testing/res_pt1000_rankT.pdf}
\caption[Testing non-parametric statistics with 1000 data points]{Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the known asymmetry of tail dependence of the C and SC copulas, and the known symmetry of tail dependence of the N and F copulas. See Appendix  \ref{Test_npa_stat} for details. $n=1000$.\label{fig_stat_testing1000}}
\end{center}
\end{figure}

@@

For bivariate data sets, surrogates were produced as follows.

- Given data $(x_i,y_i)$ for $i=1,\ldots,n$ and a 
one-parameter target copula family $\mathcal{B}(\theta)$ (here $\theta$ denotes the parameter), let $\tau$ be the
Kendall correlation of the $x_i$ with the $y_i$ and find the parameter value $\theta_\tau$ for which 
$\mathcal{B}(\theta_\tau)$ has Kendall correlation $\tau$ (this is possible for the one-parameter copula families of this 
study using the `iTau` function of the `VineCopula` package). 
- Generate data $(a_i,b_i)$, $i=1,\ldots,n$ from 
$\mathcal{B}(\theta_\tau)$. 
- Permute the ordered set $(x_1,\ldots,x_n)$ such that the permutation
$(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ has $\rank(x_{\sigma_x(i)})$ equal to $\rank(a_i)$ for all $i$, where 
$\rank(x_{\sigma_x(i)})$ is the rank of $x_{\sigma_x(i)}$ in the set $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$, and
$\rank(a_i)$ is the rank of $a_i$ in the set $(a_1,\ldots,a_n)$ (here $\sigma_x$ is a permutation of the 
indices $1,\ldots,n$). 
- Likewise permute $(y_1,\ldots,y_n)$
such that the permutation
$(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ has $\rank(y_{\sigma_y(i)})$ equal to $\rank(b_i)$ for all $i$ ($\sigma_y$ is 
another permutation of $1,\ldots,n$).
- The surrogate data set is $(x_{\sigma_x(i)},y_{\sigma_y(i)})$ for $i=1,\ldots,n$.

\noindent Our code for this algorithm is `copsurrog2d` in the 
`BIVAN` repository (https://github.com/sghosh89/BIVAN). 
Because $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ 
is a permutation of $(x_1,\ldots,x_n)$ and $(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ is a 
permutation 
of $(y_1,\ldots,y_n)$, the marginal distributions of the surrogate data are exactly the same as 
those of the original data. 
Because ranks of the surrogate data are matched to ranks of the $a_i$ and $b_i$, the
Kendall correlation of the surrogate data set will be the same as that of the $a_i$ and $b_i$, and therefore 
will be close to $\tau$ (differences arising only through sampling variation). If instead of $\theta_\tau$
a parameter value $\theta_\rho$ is used such that the Spearman correlation of $\mathcal{B}(\theta_\rho)$ is the same
as that of the $x_i$ with the $y_i$, then Spearman correlations of surrogates will very nearly equal (except for 
sampling variation) the Spearman correlation of the empirical data.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_soilCN/soilCN_bivfunctionplot.pdf}
\caption[Non-parametric tests against an N-copula null, soil C and N data]{Non parametric tests for tail dependence and other deviations from N-copula structure, for soil C and N data. As described in the main text, the values of the statistics $\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$ and $\Dsq_{l_b,u_b}$ for real data (red crosses) were compared to distributions of their values on 1000 Kendall- or Spearman-preserving N surrogates of the data (blue and green x's show 0.025 and 0.975 quantiles), separately in two comparisons for each of the ranges $(l_b,u_b)=(0,0.1),\ldots,(0.9,1)$. Whenever the red cross was outside the range given by the x's, text at the top of panels indicates the number of surrogate values the real-data value was greater than or less than. For instance, a value $>N$ (respectively, $<N$) means the value of the statistic on real data was greater than (respectively, less than) its value on $N$ surrogates. When the statistic was greater than 975 or less than 975 surrogate values, it indicates significance ($95\%$ confidence level). When $\cor$ or $\Ps$ values (respectively, $\Dsq$ values) were greater than surrogates, it means dependence in that part of the distributions was stronger than (respectively, weaker than) expected from a normal-copula null hypothesis. \label{fig_soilCN_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/BMR_results/birds/birds_numbin_10_bivfunctionplot.pdf}
\caption[Non-parametric tests against an N-copula null, bird body mass and BMR data]{Non parametric tests for tail dependence and other deviations from N-copula structure, for bird body mass and BMR data. Same format as Fig. \ref{fig_soilCN_nonparam}, see caption of that figure. \label{fig_bmr_birds_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/BMR_results/mammals/mammals_numbin_10_bivfunctionplot.pdf}
\caption[Non-parametric tests against an N-copula null, mammal body mass and BMR data]{Non parametric tests for tail dependence and other deviations from N-copula structure, for mammal body mass and BMR data. Same format as Fig. \ref{fig_soilCN_nonparam}, see caption of that figure. \label{fig_bmr_mammals_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Ceder_creek_results/2000cc_numbin_10_bivfunctionplot.pdf}
\caption[Non-parametric tests against an N-copula null, Cedar Creek data]{Non parametric tests for tail dependence and other deviations from N-copula structure, for Cedar Creek data. Same format as Fig. \ref{fig_soilCN_nonparam}, see caption of that figure.\label{fig_cc2000_nonparam}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.4 cm} (D)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Corl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{3.4 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.4 cm} (H)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Pl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_D2u_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{5.4 cm} (I) \hspace{3.4 cm} (J) \hspace{3.2 cm} (K) } \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption[Non-parametric tail statistics versus distance between locations for green spruce aphid abundance data]{Non parametric tail statistics versus great-circle distance, $D$, between sampling locations for green spruce aphid abundance data. \label{fig_aphid_count}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.4 cm} (D)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{3.4 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.4 cm} (H)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{5.4 cm} (I) \hspace{3.4 cm} (J) \hspace{3.2 cm} (K) } \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption[Non-parametric tail statistics versus distance between locations for leaf-curling plum aphid first flight data]{Non parametric tail statistics versus great-circle distance, $D$, between sampling locations for leaf-curling plum aphid first flight data. \label{fig_aphid_ff}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\textbf{ \hspace{3.4 cm} (A) \hspace{3.2 cm} (B) \hspace{3.2 cm} (C) \hspace{3.4 cm} (D)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Spearman_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Kendall_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Coru_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{3.4 cm} (E) \hspace{3.2 cm} (F) \hspace{3.2 cm} (G) \hspace{3.4 cm} (H)} \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2l_vs_D.pdf}\\
\end{center}
\textbf{ \hspace{5.4 cm} (I) \hspace{3.4 cm} (J) \hspace{3.2 cm} (K) } \\
\vspace{-0.5 cm}
\begin{center}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Corl-Coru_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_Pl-Pu_vs_D.pdf}
\includegraphics[width=4 cm]{./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u-D2l_vs_D.pdf}
\caption[Non-parametric tail statistics versus distance between locations for \textit{Ceratium furca} abundance data]{Non-parametric tail statistics versus great-circle distance, $D$, between sampling locations for \textit{Ceratium furca} abundance data. \label{fig_pns}}
\end{center}
\end{figure}
